Whittaker Models for Real Groups

### 2024-02-23 whittaker.tex
Add small comments

\renewcommand{\t}{\mathfrak t}
\newcommand{\su}{\mathfrak s\mathfrak u}
\newcommand{\g}{\mathfrak g}
\newcommand\inv{^{-1}}
\newcommand\wh{\widehat}
\newcommand{\GL}{\text{GL}}
\newcommand{\SL}{\text{SL}}
\newcommand{\SO}{\text{SO}}
\newcommand{\SU}{\text{SU}}
\newcommand{\Spin}{\text{Spin}}
\newcommand{\chGGamma}{\phantom{a}^\vee G^\Gamma}
\newcommand{\GGamma}{G^\Gamma}
\newcommand{\s}{\mathfrak s}
\newcommand{\w}{\mathfrak w}
\newcommand{\AV}{\mathrm{AV}}
\newcommand{\WF}{\mathrm{WF}}
\newcommand{\AVann}{\mathrm{AV}_{\mathrm{ann}}}
\newcommand{\GK}{\mathrm{GK}}
\newcommand{\Op}{\O_p}
\begin{document}
\title{Whittaker Models for Real Groups}
\author{Jeffrey Adams + AA}
\maketitle

@@

There are several ways to describe this bijection. We choose to compose the maps (1)$\leftrightarrow$(3)$\leftrightarrow$(4).
Here is the conclusion.

@@

We can also express (1)$\mapsto$(4) using the {\it Kostant section}.\footnote{14-II-2024: we could spell out the definition, it seems this can be done quickly as in Adams--Kaletha. }

@@

\begin{proposition}[\cite{adams_kaletha}]
Suppose $\pi$ is a generic discrete series representation. Then $\pi$ is $\w$-generic
for a unique Whittaker datum $\w$.
Write $\w=\w_X$ for some regular nilpotent element $X\in i\g(\R)$.
Then $H_\pi$ is $G(\R)$-conjugate to an element of the Kostant section of $X$.
\end{proposition}

>>>>

\renewcommand{\t}{\mathfrak t}
\newcommand{\su}{\mathfrak s\mathfrak u}
\newcommand{\g}{\mathfrak g}
\newcommand\inv{^{-1}}
\newcommand\wh{\widehat}
\newcommand{\GL}{\text{GL}}
\newcommand{\SL}{\text{SL}}
\newcommand{\SO}{\text{SO}}
\newcommand{\SU}{\text{SU}}
\newcommand{\Spin}{\text{Spin}}
\newcommand{\chGGamma}{\phantom{a}^\vee G^\Gamma}
\newcommand{\GGamma}{G^\Gamma}
\newcommand{\s}{\mathfrak s}
\newcommand{\w}{\mathfrak w}
\newcommand{\AV}{\mathrm{AV}}
\newcommand{\WF}{\mathrm{WF}}
\newcommand{\AVann}{\mathrm{AV}_{\mathrm{ann}}}
\newcommand{\GK}{\mathrm{GK}}
\newcommand{\Op}{\O_p}
\newcommand{\Kostant}[1]{\mathcal{K}(#1)}

\begin{document}
\title{Whittaker Models for Real Groups}
\author{Jeffrey Adams + AA}
\maketitle

@@

There are several ways to describe this bijection.\footnote{AA 23-II-2024: it might be nice to mention the version with the asymptotic cone of the orbit of~$H_\pi$, which is extremely clean and concrete. } We choose to compose the maps (1)$\leftrightarrow$(3)$\leftrightarrow$(4).
Here is the conclusion.

@@

We can also express (1)$\mapsto$(4) using the {\it Kostant section}. Recall that if~$X$ is a regular nilpotent element of~$\g$ and fits into an $\SL(2)$-triple $(X, H, Y)$, the Kostant section~$\Kostant{X}$ is the affine subspace $X + \mathrm{Cent}_{\g}(Y)$ of~$\g$. It depends on the choice of $\SL(2)$-triple, but if $X \in \g(\R)$, then the $G(\R)$-conjugacy class of~$\Kostant{X}$ depends only on the $G(\R)$-conjugacy class of~$X$.

@@

\begin{proposition}[\cite{adams_kaletha}]
Suppose $\pi$ is a generic discrete series representation. Then $\pi$ is $\w$-generic
for a unique Whittaker datum $\w$.
Write $\w=\w_X$ for some regular nilpotent element $X\in i\g(\R)$.
Then $H_\pi$ is $G(\R)$-conjugate to an element of the Kostant section of $X$.\footnote{AA 23-II-2024: would probably be useful to explain the connection with $\pi \mapsto \WF(\pi)$ in more detail...}
\end{proposition}
